Adaptive evolution with aneuploidy and mutation

### 2022-06-02 ms/ms.tex
revised FA histogram and added FA values

\citet{Yona2012} have suggested that aneuploidy is a transient adaptive solution, arising quickly due to increased fitness and high formation rate, but 
ultimately lost as beneficial mutations appear and the extra chromosome is lost due to the cost of aneuploidy. 
We tested this scenario by estimating $F_A$, the expected frequency of \eumt\ that arose from \anwt\ (as the average frequency of such cells at the end of 50 replicate simulations).
Surprisingly, we observe that the majority ($F_A=XX$) % TODO add number
of \eumt\ cells are a product of a direct mutation in \euwt\ cells, rather than descending from \anwt\ cells. 
This is despite the fact that the \anwt\ genotype reaches high frequencies in the population (\Cref{fig:ppc-plot}A). % TODO add number
This result is not unique to the MAP parameter estimate. 
We simulated genotype frequency dynamics using parameter samples from the posterior distribution (\Cref{fig:posterior}), and computed the posterior distribution of $F_A$ (\Cref{fig:ppc-plot}B). 
The mean $F_A$ was just XX [XX-XX 95\% CI], % TODO add number
such that if we pick up a cell from the evolved population it is more likely to have descended directly from a euploid cell than from an aneuploid cell.
As expected, the probability of \eumt\ descending from \anwt\ ($F_A$) increases with the aneuploidy rate, $\delta$, and decreases with the mutation rate, $\mu$ (\Cref{fig:ppc-plot}C and D).

>>>>

\citet{Yona2012} have suggested that aneuploidy is a transient adaptive solution, arising quickly due to increased fitness and high formation rate, but 
ultimately lost as beneficial mutations appear and the extra chromosome is lost due to the cost of aneuploidy. 
We tested this scenario by estimating $F_A$, the expected frequency of \eumt\ that arose from \anwt\ (as the average frequency of such cells at the end of 50 replicate simulations).
Surprisingly, we observe that the majority ($F_A=XX$) % TODO add number
of \eumt\ cells are a product of a direct mutation in \euwt\ cells, rather than descending from \anwt\ cells. 
This is despite the fact that the \anwt\ genotype reaches high frequencies in the population (\Cref{fig:ppc-plot}A). % TODO add number
This result is not unique to the MAP parameter estimate. 
We simulated genotype frequency dynamics using parameter samples from the posterior distribution (\Cref{fig:posterior}), and computed the posterior distribution of $F_A$ (\Cref{fig:ppc-plot}B). 
The mean $F_A$ was just 0.1758 [0.0148-0.4114 95\% CI],
such that if we pick up a cell from the evolved population it is more likely to have descended directly from a euploid cell than from an aneuploid cell.
As expected, the probability of \eumt\ descending from \anwt\ ($F_A$) increases with the aneuploidy rate, $\delta$, and decreases with the mutation rate, $\mu$ (\Cref{fig:ppc-plot}C and D).
